Approximation as Differentiation: Notes

### 2025-05-16 main/formal-structures.tex
No need to 'define' the [-,C] functor, just introduce informally before Fam(C).

\begin{definition}
Let $\Func{-}{\cat{C}}: \Set^{\op} \to \Cat$ denote the indexed category which sends any set $X$ to the
category $\Func{X}{\cat{C}}$ and any function $f: X \to Y$ to the functor $\reindex{-}{f}: \Func{Y}{\cat{C}}
\to \Func{X}{\cat{C}}$.
\end{definition}

@@

\noindent The $\partial X$ notation is intended to suggest the connection between the Grothendieck
construction and the idea of tangent spaces and derivatives. To understand how the $\partial X$ components
compose, consider any $(f, \partial f): (X, \partial X) \to (Y, \partial Y)$ and $(g, \partial g): (Y,
\partial Y) \to (Z, \partial Z)$ in $\Grothendieck{}T$. We have:

@@

>>>>

@@

\noindent The $\partial X$ notation is intended to suggest the connection between the Grothendieck
construction and the idea of tangent spaces and derivatives. To understand how the $\partial f$ components
compose, consider any $(f, \partial f): (X, \partial X) \to (Y, \partial Y)$ and $(g, \partial g): (Y,
\partial Y) \to (Z, \partial Z)$ in $\Grothendieck{}T$. We have:

@@

Of interest to us is the Grothendieck construction for $\Func{-}{\cat{C}}: \Set^{\op} \to \Cat$, the indexed
category which sends any set $X$ to the functor category $\Func{X}{\cat{C}}$ and any function $f: X \to Y$ to
the reindexing functor $- \comp f: \Func{Y}{\cat{C}} \to \Func{X}{\cat{C}}$.
